Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-04-27 mu/article/article.tex
sab

\ref{fig:up-vx-comp-rtp-1} and \ref{fig:up-vy-comp-rtp-1} we present the results
polarization angle to $40^{\circ}$ for the \emph{up} structure vs photon energy
and the corresponding polar $\varphi$ and azimuthal $\theta$ angles. In the
bottom frames of Figs. \ref{fig:up-vx-comp-rtp-1} and \ref{fig:up-vx-comp-rtp-1}
we present the decomposition of $|\mathcal{V}^{\mathrm{x}}|$ and
$|\mathcal{V}^{\mathrm{y}}|$ in the corresponding $\mathcal{V}^{\mathrm{xx}}$,
$\mathcal{V}^{\mathrm{xy}}$, $\mathcal{V}^{\mathrm{xz}}$ and

@@

angles of $\varphi=47.4$ and $\theta=212.5$, respectively. Also we found that. Now, from Fig.
\ref{fig:up-vy-comp-rtp-1} we have that for the same incoming beam energy the
$yx$ and $yy$ components have less contributions for the total response than the
$yz$ having values of $\mathcal{V}^{\mathrm{yx}}= -7.9$\,Km/s
$\mathcal{V}^{\mathrm{yy}}=  8.5$\,Km/s $\mathcal{V}^{\mathrm{yz}}= 87.1$\,Km/s
and resulting in a value of the total response of
$|\mathcal{V}^{\mathrm{y}}|=87.9$\,Km/s with polar and azimuthal angles
$\varphi=7.6$ $\theta=132.6$, respectively.

@@

Also there is another zone of interest, depicted in Fig. \ref{fig:up-3d-2},
where a local maximum is obtained for energies from 0.95\,eV to 0.99\,eV and
same polarization angles. From Figs. \ref{fig:up-3d-vx-2} ad 
\ref{fig:up-3d-vy-2} we have that $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}
^{\mathrm{y}}|$ reach values of 10\,Km/s and 50\,Km/s, respectively.

>>>>

In Figs. \ref{fig:up-vx-comp-rtp-1} and \ref{fig:up-vy-comp-rtp-1} we present
the results for $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$
fixing the polarization angle to $\alpha=40^{\circ}$ for the \emph{up} structure
vs photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
angles. In the bottom frames of Figs. \ref{fig:up-vx-comp-rtp-1} and 
\ref{fig:up-vx-comp-rtp-1} we present the decomposition of

@@

angles of $\varphi=47.4$ and $\theta=212.5$, respectively.
Now, from Fig. \ref{fig:up-vy-comp-rtp-1} we have that the $yx$ and $yy$
components have less contributions for the total response than the $yz$ and for
the same incoming beam energy have values of $\mathcal{V}^{\mathrm{yx}}=
-7.9$\,Km/s $\mathcal{V}^{\mathrm{yy}}= 8.5$\,Km/s, and
$\mathcal{V}^{\mathrm{yz}}= 87.1$\,Km/s resulting in a value of the total
response of $|\mathcal{V}^{\mathrm{y}}|=87.9$\,Km/s with polar and azimuthal
angles $\varphi=7.6$ $\theta=132.7$, respectively.

@@

Also there is another energy range of interest, from 1.80\,eV to 2.10\,eV and
same polarization angle $\alpha=40^{\circ}$ depicted in Fig. \ref{fig:up-3d-2},
where two local maxima are obtained the \emph{up} structure. Again, in the
bottom frame of Fig. \ref{fig:up-vx-comp- rtp-2} we have the three components
$\mathcal{V}^{\mathrm{xx}}$, $\mathcal{V}^{\mathrm{xy}}$, and
$\mathcal{V}^{\mathrm{xz}}$ corresponding to $|\mathcal{V}^{\mathrm{x}}|$ and in
the bottom frame of Fig. \ref{fig:up-vy-comp-rtp-2} the three components $\mathcal{V}^{\mathrm{yx}}$, $\mathcal{V}^{\mathrm{yy}}$, and $\mathcal{V}^{\mathrm{yz}}$ corresponding to $|\mathcal{V}^{\mathrm{y}}|$
